---
title: "**Eye tracking: Gender, Medical Leave, and Supervisors (after meeting with Kevin)**"
author: "**Motro et al. 2020 - Working Paper**"
date: '`r Sys.Date()`'
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{rotating}
- \usepackage{longtable}
- \usepackage{gensymb}
- \usepackage{amsfonts}
- \usepackage{amsmath}
- \DeclareUnicodeCharacter{2588}{$\bullet$}
output:
  pdf_document:
    toc: true
    fig_height: 10
    fig_width: 15
fontsize: 10pt
---

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)
library(ggplot2)
library(car)
library(sjmisc)  # for sample data
library(tidyverse)
library(lattice)
library(gmodels)
library("ggpubr")
library(Amelia)
library(rmarkdown)
library(dplyr)
library(plyr)
library(Rmisc)
library(corrr)
library(psych)
library(lattice)
library(Rmisc)
library(psych)
library(Hmisc)
library(gridExtra)
library(lme4)
library(pander)
library(interactions)
library(lmerTest)
library(emmeans)
library(tinytex)


## Global options
options(scipen=999)
options(digits=8)
options(round=4)
options(max.print=10000)
opts_chunk$set(echo=FALSE,
               cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


\pagebreak

# ***Open data***

## *Open*

\vspace{\baselineskip}

```{r Age, echo = FALSE}
prof <- rio::import(file = "/Users/andreapittarello/Dropbox/Eye-Tracking Data/May_Medical_Data/Behavior_and_eye_movements_May_24_2020.xlsx", which = 1L)

library(pander)
library(pastecs)

```

\vspace{\baselineskip}


# ***Selection: Only Experimental Trials - all combinations***
As can be seen, overall people prefer F over M when the profiles are different. 
\vspace{\baselineskip}

```{r Choices1, echo=FALSE}
prof.exp<-subset(prof, Trial_Type=="Experimental")
Cost.se<- na.omit(summarySE(prof.exp, measurevar="Select", 
                            groupvars=c("Combination_type","Gender"),
                            na.rm=TRUE))
pander(Cost.se)

figure<-ggplot(Cost.se, aes(x=Combination_type, y=Select, 
														colour=Gender,shape=Gender)) + 
	geom_bar(position=position_dodge(), stat="identity",
					 aes(fill=Gender),colour="Black",
					 size=.5) +  
	xlab("\nCombination Type") +
	ylab("% of choice\n") +
	coord_cartesian(ylim=c(0,1)) + 
	scale_y_continuous(breaks=seq(0,1,.2))+
	theme_bw()+
	ggtitle("Likelihood of choosing (in %)") +
	theme_bw()+theme(panel.grid.minor=element_line(colour="White"))+
	theme(panel.grid.major=element_line(colour="White"))+
	theme(legend.position="bottom")+
	theme(legend.key=element_rect(colour="White"))+
	theme(legend.key=element_rect(colour="White"))+
	theme(panel.border=element_rect(colour="White"))+
	theme(axis.line.x = element_line(colour = 'black', size=.5))+
	theme(axis.line.y = element_line(colour = 'black', size=.5))+
	theme(axis.text=element_text(size=16))+
	theme(axis.title=element_text(size=16,face="bold"))+
	theme(legend.text=element_text(size=16))+
	theme(legend.title=element_blank())+
	theme(plot.title=element_text(size=12,face="bold"))+
	theme(axis.line.y = element_line(colour = 'black', size=.5),
				axis.line.x = element_line(colour = 'black', size=.5))
library(jtools)
figure + scale_fill_grey(start = .3, end = .7) + theme_apa(legend.pos = "topright",
																													 legend.font.size = 16,
																													 x.font.size = 16, y.font.size = 16) +
	theme(axis.text.x = element_text(size = 16)) + theme(axis.text.y = element_text(size = 16))
#figure + scale_fill_hue(l=35, c=55)
#figure + scale_fill_manual(values=c("grey", "firebrick"))
```

# ***Selection: Only Filler Trials - all combinations***

\vspace{\baselineskip}

```{r Choices2, echo=FALSE}
prof.fill<-subset(prof, Trial_Type=="Filler")

Cost.se<- na.omit(summarySE(prof.fill, measurevar="Select", 
                            groupvars=c("Combination_type","Gender"),
                            na.rm=TRUE))
pander(Cost.se)
```

# ***GLMER on choice: Experimental Trials and Different combinations***
The regression shows a strong main effect of gender. Preference for F over M when combinations are different. 
\vspace{\baselineskip}

```{r Choices3, echo=FALSE}
prof.dif<-subset(prof.exp,Combination_type=="different")

m <- glmer(Select ~ Gender + (1 | Participant), data = prof.dif, family = binomial)
Anova(m, type =3)
summ(m)
```

# ***Choice by Gender of the candidate and leave Experimental Trials and Different combinations***
Here, we look at whether the preference depends on type of leave. 
\vspace{\baselineskip}

```{r Choices4, echo=FALSE}
prof.dif.only.leave <- subset(prof.dif,AOI=="leave")

Cost.se<- na.omit(summarySE(prof.dif.only.leave, measurevar="Select", 
                            groupvars=c("Content_of_AOI","Gender"),
                            na.rm=TRUE))
pander(Cost.se)
figure<-ggplot(Cost.se, aes(x=Gender, y=Select, 
														colour=Content_of_AOI,shape=Content_of_AOI)) + 
	geom_bar(position=position_dodge(), stat="identity",
					 aes(fill=Content_of_AOI),colour="Black",
					 size=.5) +  
	xlab("\nType of leave") +
	ylab("% of choice\n") +
	coord_cartesian(ylim=c(0,1)) + 
	scale_y_continuous(breaks=seq(0,1,.2))+
	theme_bw()+
	ggtitle("Likelihood of choosing based on gender and type of leave (%) ") +
	theme_bw()+theme(panel.grid.minor=element_line(colour="White"))+
	theme(panel.grid.major=element_line(colour="White"))+
	theme(legend.position="bottom")+
	theme(legend.key=element_rect(colour="White"))+
	theme(legend.key=element_rect(colour="White"))+
	theme(panel.border=element_rect(colour="White"))+
	theme(axis.line.x = element_line(colour = 'black', size=.5))+
	theme(axis.line.y = element_line(colour = 'black', size=.5))+
	theme(axis.text=element_text(size=16))+
	theme(axis.title=element_text(size=16,face="bold"))+
	theme(legend.text=element_text(size=16))+
	theme(legend.title=element_blank())+
	theme(plot.title=element_text(size=12,face="bold"))+
	theme(axis.line.y = element_line(colour = 'black', size=.5),
				axis.line.x = element_line(colour = 'black', size=.5))
library(jtools)
figure + scale_fill_grey(start = .3, end = .7) + theme_apa(legend.pos = "topright",
																													 legend.font.size = 16,
																													 x.font.size = 16, y.font.size = 16) +
	theme(axis.text.x = element_text(size = 16)) + theme(axis.text.y = element_text(size = 16))
#figure + scale_fill_hue(l=35, c=55)
#figure + scale_fill_manual(values=c("grey", "firebrick","blue"))
```

# ***GLMER: Gender of the candidate by leave Experimental Trials and Different combinations and contrasts below***
This model tests the effect of type of leave and gender on likelihood of choosing.
As can be seen, we have a main effect of gender and type of leave. No interaction.
Contrasts are below for each comparison. Overall, all leaves are different. People choose more frequently people on parental vs. no leave, parental vs. medical and parental vs. no leave. 
The effect of gender is the same as above. Note that the contrasts for the interaction are for illustrative purposes since the interaction was n.s. 
\vspace{\baselineskip}

```{r Choices5, echo=FALSE}
m <- glmer(Select ~ Gender+Content_of_AOI +Gender*Content_of_AOI+ (1 | Participant), data = prof.dif.only.leave, family = binomial)
Anova(m,type =3)
summ(m)

cat_plot(m, pred = Content_of_AOI, modx = Gender,geom = "bar", interval = TRUE)

emm = emmeans(m, ~ Content_of_AOI * Gender)
pairs(emm, simple = "each")
emm = emmeans(m, ~ Content_of_AOI)
pairs(emm, simple = "each")
emm = emmeans(m, ~ Gender)
pairs(emm, simple = "each")

```

# ***Descriptive: Percentage of attention on the Type of Leave AOI (all fixations)***
This below shows the relative amount of attention on the leave box by gender, type of leave, and choice (chosen vs. not chosen)
\vspace{\baselineskip}
```{r Choices6, echo=FALSE}
Cost.se<- na.omit(summarySE(prof.dif.only.leave, measurevar="Percentage", 
														groupvars=c("Gender","Content_of_AOI","Select"),
														na.rm=TRUE))
pander(Cost.se)

```



# ***Regression: Percentage of attention on the Type of Leave AOI (all fixations)***
The regression has percentage of attention as DV, and choice, leave type, and gender as IV.
We can see that there is an interaction between leave type and choice. No interaction with gender (we did not have it either with choice - see above.)
Plot and contrasts are below

\vspace{\baselineskip}
```{r Choices7, echo=FALSE}
m<-lmer(Percentage ~ Content_of_AOI*Select*Gender+ (1|Participant),data=prof.dif.only.leave)
summ(m)
Anova(m,type = 3)


# Interaction Content by Selection ##
Cost.se<- na.omit(summarySE(prof.dif.only.leave, measurevar="Percentage", 
														groupvars=c("Content_of_AOI","Select"),
														na.rm=TRUE))
pander(Cost.se)
ggplot(Cost.se, aes(x=Select, y=Percentage, fill=Content_of_AOI)) + 
	geom_bar(position=position_dodge(), stat="identity",
					 colour="black", # Use black outlines,
					 size=.3) +      # Thinner lines
	geom_errorbar(aes(ymin=Percentage-se, ymax=Percentage+se),
								size=.4,    # Thinner lines
								width=.3,
								position=position_dodge(.9)) +
	theme(axis.line.x = element_line(colour = 'white', size=.2))+
	theme(axis.line.y = element_line(colour = 'black', size=.2))+
	theme(axis.text=element_text(size=24))+
	theme(axis.title=element_text(size=16,face="bold"))+
	theme(legend.text=element_text(size=34))+
	theme(legend.title=element_blank())+
	theme(plot.title=element_text(size=12,face="bold"))+
	xlab("Choice (0 not chosen, 1 chosen)") +
	ylab("\nProportion of Attention (in %)") +
	#scale_fill_hue(name="Alternative", # Legend label, use darker colors
	#              breaks=c("Competitor", "Target"),
	#             labels=c("Competitor", "Target")) +
	ggtitle("Proportion of attention on the type of leave AOI by Choice") +
	coord_cartesian(ylim=c(0,100 )) + 
	scale_y_continuous(breaks=seq(0, 100, 10))+
	scale_fill_manual(values=c("white", "grey","red"))
	#scale_y_continuous(breaks=0:7) +
	#theme_base() + facet_wrap(~Select)


emm = emmeans(m, ~ Content_of_AOI*Select)
pairs(emm, simple = "each")
```

#***Regression: Fix duration on type of leave***
The regression has fixateion duration on type of leave as DV, and choice, leave type, and gender as IV.
We can see that there is an interaction between leave type and choice. No interaction with gender (we did not have it either with choice - see above.)
Plot and contrasts are below
\vspace{\baselineskip}

```{r Choices8, echo=FALSE}

m<-lmer(Fix_Dur ~ Content_of_AOI*Select*Gender+ (1|Participant),data=prof.dif.only.leave)
summ(m)
Anova(m,type = 3)

Cost.se<- na.omit(summarySE(prof.dif.only.leave, measurevar="Fix_Dur", 
														groupvars=c("Content_of_AOI","Select"),
														na.rm=TRUE))
pander(Cost.se)
library(ggthemes)
ggplot(Cost.se, aes(x=Select, y=Fix_Dur, fill=Content_of_AOI)) + 
	geom_bar(position=position_dodge(), stat="identity",
					 colour="black", # Use black outlines,
					 size=.3) +      # Thinner lines
	geom_errorbar(aes(ymin=Fix_Dur-se, ymax=Fix_Dur+se),
								size=.4,    # Thinner lines
								width=.3,
								position=position_dodge(.9)) +
	theme(axis.line.x = element_line(colour = 'white', size=.2))+
	theme(axis.line.y = element_line(colour = 'black', size=.2))+
	theme(axis.text=element_text(size=24))+
	theme(axis.title=element_text(size=16,face="bold"))+
	theme(legend.text=element_text(size=34))+
	theme(legend.title=element_blank())+
	theme(plot.title=element_text(size=12,face="bold"))+
	xlab("Choice") +
	ylab("\nFixation Durations on leave type") +
	#scale_fill_hue(name="Alternative", # Legend label, use darker colors
	#              breaks=c("Competitor", "Target"),
	#             labels=c("Competitor", "Target")) +
	ggtitle("Overall fixations on type of leave") +
	coord_cartesian(ylim=c(0,500 )) + 
	scale_y_continuous(breaks=seq(0, 500, 100))+
	scale_fill_manual(values=c("white", "grey","red"))+
	#scale_y_continuous(breaks=0:7) +
	theme_base() 
emm = emmeans(m, ~ Content_of_AOI*Select)
pairs(emm, simple = "each")
```

#***Regression: Percentage x Leave type predicting choice***
The regression has choice as DV. Predictors are percentage of attention on leave, type of leave, and gender. 
As can be seen, there is an interaction between type of leave and percentage predicting choice. The plot is below together with slope analysis. 
\vspace{\baselineskip}

```{r Choices9, echo=FALSE}

library(jtools)
m<-lmer(Select ~ Content_of_AOI*Percentage*Gender+ (1|Participant),data=prof.dif.only.leave)
summ(m)
Anova(m,type = 3)

# interaction content by percentage prediting choice #
library(interactions)
sim_slopes(m, pred =Percentage, modx=Content_of_AOI, Johnson_neyman = FALSE)
interact_plot(m, pred = Percentage, modx = Content_of_AOI,interval = TRUE)

# three way plot DV = percentage of attention, IV = gender IV1 = leave #
Cost.se<- na.omit(summarySE(prof.dif.only.leave, measurevar="Percentage", 
														groupvars=c("Content_of_AOI","Select","Gender"),
														na.rm=TRUE))
pander(Cost.se)
ggplot(Cost.se, aes(x=Content_of_AOI, y=Percentage, fill=Gender)) + 
	geom_bar(position=position_dodge(), stat="identity",
					 colour="black", # Use black outlines,
					 size=.3) +      # Thinner lines
	geom_errorbar(aes(ymin=Percentage-se, ymax=Percentage+se),
								size=.4,    # Thinner lines
								width=.3,
								position=position_dodge(.9)) +
	theme(axis.line.x = element_line(colour = 'white', size=.2))+
	theme(axis.line.y = element_line(colour = 'black', size=.2))+
	theme(axis.text=element_text(size=24))+
	theme(axis.title=element_text(size=16,face="bold"))+
	theme(legend.text=element_text(size=34))+
	theme(legend.title=element_blank())+
	theme(plot.title=element_text(size=12,face="bold"))+
	xlab("Choice (0 not chosen, 1 chosen)") +
	ylab("\nProportion of Attention (in %)") +
	#scale_fill_hue(name="Alternative", # Legend label, use darker colors
	#              breaks=c("Competitor", "Target"),
	#             labels=c("Competitor", "Target")) +
	ggtitle("Proportion of attention on the type of leave AOI by Choice") +
	coord_cartesian(ylim=c(0,100 )) + 
	scale_y_continuous(breaks=seq(0, 100, 10))+
	scale_fill_manual(values=c("white", "grey","red"))+ facet_wrap(~Select)
	#scale_y_continuous(breaks=0:7) +
	#theme_base() + facet_wrap(~Select)



```

